### 2022-05-06 paper/ase22/tables/test-results-table.tex
revise table3

\resizebox{\textwidth}{!}{
\begin{tabular}{p{4cm}||p{1cm}p{2cm}p{1cm}p{2cm}p{1cm}p{2cm}p{2cm}}

@@

\tLc & \parbox{1cm}{\tNumBlSents} & \parbox{1cm}{\tNumBlFail} & \parbox{1cm}{\tNumSeeds} & \parbox{1.5cm}{\tNumSeedFail} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\tNumExpFail} & \parbox{1.5cm}{\tNumPasstoFail}\\

@@

\multirow{3}{*}{\parbox{4cm}{LC1: \UseMacro{test-results-lc0}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc0-num-sents}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc0-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc0-num-seeds}}

@@

 & \multirow{3}{*}{\UseMacro{test-results-lc0-num-exps}}

@@

 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc0-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc0-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc0-num-exp-fail}

@@

 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc0-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc0-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc0-num-exp-fail}

@@

\multirow{3}{*}{\parbox{4cm}{LC2: \UseMacro{test-results-lc1}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc1-num-sents}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc1-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc1-num-seeds}}

@@

 & \multirow{3}{*}{\UseMacro{test-results-lc1-num-exps}}

@@

 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc1-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc1-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc1-num-exp-fail}

@@

 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc1-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc1-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc1-num-exp-fail}

@@

\multirow{3}{*}{\parbox{4cm}{LC3: \UseMacro{test-results-lc2}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc2-num-sents}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc2-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc2-num-seeds}}

@@

 & \multirow{3}{*}{\UseMacro{test-results-lc2-num-exps}}

@@

 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc2-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc2-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc2-num-exp-fail}

@@

 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc2-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc2-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc2-num-exp-fail}

@@

\multirow{3}{*}{\parbox{4cm}{LC4: \UseMacro{test-results-lc3}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc3-num-sents}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc3-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc3-num-seeds}}

@@

 & \multirow{3}{*}{\UseMacro{test-results-lc3-num-exps}}

@@

 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc3-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc3-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc3-num-exp-fail}

@@

 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc3-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc3-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc3-num-exp-fail}

@@

\multirow{3}{*}{\parbox{4cm}{LC5: \UseMacro{test-results-lc4}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc4-num-sents}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc4-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc4-num-seeds}}

@@

 & \multirow{3}{*}{\UseMacro{test-results-lc4-num-exps}}

@@

 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc4-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc4-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc4-num-exp-fail}

@@

 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc4-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc4-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc4-num-exp-fail}

@@

\multirow{3}{*}{\parbox{4cm}{LC6: \UseMacro{test-results-lc5}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc5-num-sents}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc5-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc5-num-seeds}}

@@

 & \multirow{3}{*}{\UseMacro{test-results-lc5-num-exps}}

@@

 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc5-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc5-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc5-num-exp-fail}

@@

 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc5-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc5-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc5-num-exp-fail}

@@

\multirow{3}{*}{\parbox{4cm}{LC7: \UseMacro{test-results-lc6}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc6-num-sents}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc6-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc6-num-seeds}}

@@

 & \multirow{3}{*}{\UseMacro{test-results-lc6-num-exps}}

@@

 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc6-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc6-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc6-num-exp-fail}

@@

 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc6-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc6-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc6-num-exp-fail}

@@

\multirow{3}{*}{\parbox{4cm}{LC8: \UseMacro{test-results-lc7}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc7-num-sents}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc7-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc7-num-seeds}}

@@

 & \multirow{3}{*}{\UseMacro{test-results-lc7-num-exps}}

@@

 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc7-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc7-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc7-num-exp-fail}

@@

 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc7-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc7-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc7-num-exp-fail}

@@

\multirow{3}{*}{\parbox{4cm}{LC9: \UseMacro{test-results-lc8}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc8-num-sents}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc8-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc8-num-seeds}}

@@

 & \multirow{3}{*}{\UseMacro{test-results-lc8-num-exps}}

@@

 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc8-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc8-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc8-num-exp-fail}

@@

 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc8-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc8-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc8-num-exp-fail}

@@

\multirow{3}{*}{\parbox{4cm}{LC10: \UseMacro{test-results-lc9}}}
 & \multirow{3}{*}{\UseMacro{test-results-bl-lc9-num-sents}}
 & BERT$\colon$\UseMacro{test-results-bl-model0-lc9-num-fail}
 & \multirow{3}{*}{\UseMacro{test-results-lc9-num-seeds}}

@@

 & \multirow{3}{*}{\UseMacro{test-results-lc9-num-exps}}

@@

 & & RoBERTa$\colon$\UseMacro{test-results-bl-model1-lc9-num-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc9-num-seed-fail}
 & & RoBERTa$\colon$\UseMacro{test-results-model1-lc9-num-exp-fail}

@@

 & & dstBERT$\colon$\UseMacro{test-results-bl-model2-lc9-num-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc9-num-seed-fail}
 & & dstBERT$\colon$\UseMacro{test-results-model2-lc9-num-exp-fail}

>>>>

\resizebox{0.9\textwidth}{!}{
\begin{tabular}{p{8.5cm}||cclll}

@@

\tLc & \parbox{1cm}{\tNumSeeds} & \parbox{1cm}{\tNumExps} & \parbox{1.5cm}{\centering\tNumSeedFail} & \parbox{1.5cm}{\centering\tNumExpFail} & \parbox{1.5cm}{\centering\tNumPasstoFail}\\

@@

\multirow{3}{*}{\parbox{8.5cm}{LC1: \UseMacro{test-results-lc0}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc0-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc0-num-exps}}

@@

@@

 & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc0-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc0-num-exp-fail}

@@

 & & & dstBERT$\colon$\UseMacro{test-results-model2-lc0-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc0-num-exp-fail}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC2: \UseMacro{test-results-lc1}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc1-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc1-num-exps}}

@@

@@

 & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc1-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc1-num-exp-fail}

@@

 & & & dstBERT$\colon$\UseMacro{test-results-model2-lc1-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc1-num-exp-fail}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC3: \UseMacro{test-results-lc2}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc2-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc2-num-exps}}

@@

@@

 & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc2-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc2-num-exp-fail}

@@

 & & & dstBERT$\colon$\UseMacro{test-results-model2-lc2-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc2-num-exp-fail}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC4: \UseMacro{test-results-lc3}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc3-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc3-num-exps}}

@@

@@

 & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc3-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc3-num-exp-fail}

@@

 & & & dstBERT$\colon$\UseMacro{test-results-model2-lc3-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc3-num-exp-fail}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC5: \UseMacro{test-results-lc4}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc4-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc4-num-exps}}

@@

@@

 & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc4-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc4-num-exp-fail}

@@

 & & & dstBERT$\colon$\UseMacro{test-results-model2-lc4-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc4-num-exp-fail}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC6: \UseMacro{test-results-lc5}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc5-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc5-num-exps}}

@@

@@

 & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc5-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc5-num-exp-fail}

@@

 & & & dstBERT$\colon$\UseMacro{test-results-model2-lc5-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc5-num-exp-fail}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC7: \UseMacro{test-results-lc6}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc6-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc6-num-exps}}

@@

@@

 & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc6-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc6-num-exp-fail}

@@

 & & & dstBERT$\colon$\UseMacro{test-results-model2-lc6-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc6-num-exp-fail}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC8: \UseMacro{test-results-lc7}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc7-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc7-num-exps}}

@@

@@

 & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc7-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc7-num-exp-fail}

@@

 & & & dstBERT$\colon$\UseMacro{test-results-model2-lc7-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc7-num-exp-fail}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC9: \UseMacro{test-results-lc8}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc8-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc8-num-exps}}

@@

@@

 & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc8-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc8-num-exp-fail}

@@

 & & & dstBERT$\colon$\UseMacro{test-results-model2-lc8-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc8-num-exp-fail}

@@

\multirow{3}{*}{\parbox{8.5cm}{LC10\&11: \UseMacro{test-results-lc9}}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc9-num-seeds}}
 & \multirow{3}{*}{\centering\UseMacro{test-results-lc9-num-exps}}

@@

@@

 & & & RoBERTa$\colon$\UseMacro{test-results-model1-lc9-num-seed-fail}
 & RoBERTa$\colon$\UseMacro{test-results-model1-lc9-num-exp-fail}

@@

 & & & dstBERT$\colon$\UseMacro{test-results-model2-lc9-num-seed-fail}
 & dstBERT$\colon$\UseMacro{test-results-model2-lc9-num-exp-fail}
